Appendix 4: Model Comparison Code For Manuscript

### 2025-11-12 modelcomparison_code.Rmd
2 decimals to corfig

pt2 <- ggcorrplot(
  #compute correlatins from normalised values
  cor(tmp,use="pairwise.complete.obs"),
  show.diag = FALSE,
  outline.color = "white",
  p.mat = cor_pmat(tmp,use="pairwise.complete.obs"),
  sig.level=0.01,
  #insig = "",
  lab=TRUE,
  lab_size = 3,
  show.legend = TRUE,
  tl.cex = 10,
  digits = 1
 )

>>>>

pt2 <- ggcorrplot(
  #compute correlatins from normalised values
  cor(tmp,use="pairwise.complete.obs"),
  show.diag = FALSE,
  outline.color = "white",
  p.mat = cor_pmat(tmp,use="pairwise.complete.obs"),
  sig.level=0.01,
  #insig = "",
  lab=TRUE,
  lab_size = 2,
  show.legend = TRUE,
  tl.cex = 10,
  digits = 2
 )
